---
title: "easypar"
author: "Qingjian Chen"
date: "2021/1/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## easypar: Running R in batch

The easypar R package allows you to:

Run R functions in a parallel fashion in a trivial way.

1. Easily switch between parallel and serial executions of the same calls (at runtime).

2. Save results of parallel computation as far as they are produced (i.e., cache).

## Install

see: https://github.com/caravagn/easypar

```{r cars} 
if( !require(easypar) ){
devtools::install_github("caravagn/easypar")
}
```

## Examples:

Make a new function **test**, combined input text and output them.

```{r}

merge_text = function(x){
  paste0(x, collapse = "_")
}


test = function(i, label1, label2){
  text = merge_text( c(i, label1, label2))
  print(text)
}

label1 = "label1"
label2 = "lable2"

test(1, label1, label2)
#"1_label1_lable2"
```

We store them in a list where each position is a full set of parameters that we want to pass to each calls to f (list of lists), named according to the actual parameter names.

```{r}
inputs = lapply(1:10, function(x) list(i = x, label1 = label1, label2 = label2) )
library(easypar)

```

easypar provides a single function that takes as input f, its list of inputs and some execution parameters for the type of execution requested. The simplest call runs f in parallel, without seeing any output and just receiving the return values in a list as follows

#### parameters of easypar::run

***(1) export***: export functions defined by Environment. for examples, function **merge_text** in the examples.

***(2) packages***: the import packages. 

```{r}
runs = easypar::run(FUN = test, 
             PARAMS = lapply(1:5, function(x) list(i = x, label1 = label1, label2 = label2) ) ,
             parallel = TRUE, 
             outfile = NULL,
             export = c("merge_text"),
             packages = "tidyverse",
             filter_errors = FALSE
             )

runs

numErrors(runs)

```


